Deep Probabilistic Models for Camera Geo-Calibration

### 2018-07-31 chapters/introduction/introduction.tex
minor change

For many applications, knowing when, where, and in which direction a
picture was taken is important to understand the world. We refer to 
such a vision task as {\em geo-calibration}.
In current work of geo-calibration, most algorithms are
deterministic, which means they output fixed solutions. Deterministic
systems may seem straight-forward but they also have some 
drawbacks: 1) Deterministic systems can not handle uncertainties in
the real world very well. 2) they are not
friendly to applications developed with graphic models that are
interfaced with their outputs. To address these problems, We propose
to build probabilistic models for camera geo-calibration.

Beside geo-calibration, this thesis also studies the possibility to
learn high-level image representations with help of geographic
information. In one of our work, we demonstrate that we are able to
learn geo-temporal feature representations of image with geographic
locations and capture time. In another work, knowing the geographic
location, we transfer the learned knowledge of a CNN for ground image
segmentation to another CNN designed for overhead image segmentation.

@@

\subsection{Cross-view Imagery}
Since the cross-view imagery plays an important role in geolocalization,
we spare an separate section to introduce it. A cross-view image
pair consists of a ground-view image and an overhead image at the
same location. In some cases, the ground/overhead images are also
aligned in orientation.
Specifically, Study of the overhead imagery has been long started.
Efforts have been made to automate overhead image analysis. As early
as 1970~\cite{idelsohn1970learning} methods were introduced for
classifying terrain types from a single overhead image, with the goal
of automatically generating terrain maps.  Similarly, in 1976 Bajcsy
et al.~\cite{bajcsy1976computer} described a system for recognizing
roads, intersections, and other road-like objects in overhead imagery.
However, as overhead imaging differs drastically from ground-level
imaging, the majority of techniques that have been developed have
occurred independently and in task-specific ways~\cite{Rozen}.
Benefited from the fast growing monitoring satellite market, overhead
imagery grows fast nowadays. Microsoft BingMap provides public access
to their overhead image database with various resolution options.
Given the geographic information of the ground image, we are able to
obtain the corresponding overhead images to form the geo-orientation
aligned cross-view image pairs.
Given the fact that overhead imagery has much larger earth coverage
and better registered in geographic locations, many geo-localization
approaches~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
extract the overhead features as reference database for
geo-localization.

@@

\section{Our Approach}
We divide our approach in two steps. First, we propose a general
probabilistic model to jointly estimate the geo-calibration
parameters. The key for the success of this model is to construct good
constraint functions that describe the fitness between the calibration
parameters and the images. Under this guidance we dismantle the full
geo-calibration into several partial geo-calibration tasks, each of
which provides a constraint function that could fit into our general
model. The architecture of our approaches refers to
\figref{intro:architecture}.

>>>>

For many applications, knowing when, where, and in which direction a
picture was taken is important to understand the world. We refer to 
such a vision task as {\em geo-calibration}.
In current work of geo-calibration, most algorithms are
deterministic, which means they output fixed solutions. Deterministic
systems may seem straight-forward but they also have some 
drawbacks: 1) Deterministic systems can not handle uncertainties in
the real world very well. 2) They are not
friendly to graphic model applications.
To address these problems, We propose to build probabilistic models
for camera geo-calibration.

Beside geo-calibration, this thesis also studies the possibilities of
learning high-level image representations with the help of geographic
information. In one of our work, we demonstrate that we are able to
learn geo-temporal feature representations of image with geographic
locations and image timestamps. In another work, we exploit image geographic
locations to transfer the learned knowledge of a CNN for ground image
semantic segmentation to another CNN designed for overhead image
semantic segmentation.

@@

\subsection{Cross-view Imagery}
Since the cross-view imagery plays an important role in geolocalization,
we spare an separate section to discuss it. A cross-view image
pair consists of a ground-view image and an overhead image at the
same location. In some cases, two images are also aligned in
orientation.
Specifically, Study of the overhead imagery has been long started.
Efforts have been made to automate overhead image analysis. As early
as 1970~\cite{idelsohn1970learning} methods were introduced for
classifying terrain types from a single overhead image, with the goal
of automatically generating terrain maps.  Similarly, in 1976 Bajcsy
et al.~\cite{bajcsy1976computer} described a system for recognizing
roads, intersections, and other road-like objects in overhead imagery.
However, as overhead imaging differs drastically from ground-level
imaging, the majority of techniques that have been developed have
occurred independently and in task-specific ways~\cite{Rozen}.
Benefited from the fast growing monitoring satellite market, overhead
imagery grows fast nowadays. Microsoft BingMap provides public access
to their overhead image database with various resolution options.
Given the geographic information of the ground image, we are able to
obtain the corresponding overhead images to form the geo-orientation
aligned cross-view image pairs.
Given the fact that overhead imagery has much larger earth coverage
and better registered in geographic locations, many geo-localization
approaches~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
extract the overhead features as reference database for
geo-localization.

@@

\section{Our Approach}
Our approach consists of two big steps. First, we propose a general
probabilistic model to jointly estimate the geo-calibration
parameters. The key for the success of this model is to construct good
constraint functions which describe the fitness between the calibration
parameters and the images. As the second step of our approach, we
dismantle the full geo-calibration into several partial
geo-calibration tasks, each of which could provides a strong constraint
function that fit in the general model. The architecture of
our approaches refers to
\figref{intro:architecture}.
